XPath Agent: An Efficient XPath Programming Agent Based on LLM for Web Crawler

### 2024-10-28 paper/main.tex
add contribution

\author{
Li Yu \\ \\ \\ lijingyu68@gmail.com
\and
Bryce Wang \\ Stanford University  \\ brycewang2018@gmail.com
\and
Hazul \\ Research Dept.\\
                Science City, Sci 88088 \\ yvo@science.rdept.net
}

@@

Scrolling, navigating, back and forward through the webpage to generate XPath queries is a nature way for human. But for LLM, this process is time-consuming and computationally expensive.

@@

We assuming there are 3 core reasons why LLMs are not efficient in generating XPath queries. Firstly, LLMs are not designed to generate XPath queries. They are designed to understand and generate human-like text. Secondly, web pages are lengthy and complex, full of task unrelated information. Those information distract the LLMs from generating the correct XPath queries. Thirdly, a good XPath query should be generalizable across different web pages. However, LLMs are context limited, which means they can only generate XPath queries based on the context they have seen.

Based on the above insights, we propose a novel approach to generate XPath queries using LLMs. Our approach is designed to be efficient, accurate, and generalizable. We aim to reduce the number of steps required to generate a well-crafted XPath query, reduce the computational overhead, and improve the generalizability of the XPath queries generated by LLMs.

@@

>>>>

\author{
Li Yu \\ \\ lijingyu68@gmail.com
\and
Bryce Wang \\ Stanford University  \\ brycewang2018@gmail.com
\and
Hazul \\ Research Dept.\\
                Science City, Sci 88088 \\ yvo@science.rdept.net
}

@@

Scrolling, navigating, back and forward through webpages to program XPath queries is a nature way for human. But for LLM, this process is time-consuming and computationally expensive. We expect LLM can do better and efficient.

@@

We assuming there are 3 core reasons why LLMs are not efficient in generating XPath queries. Firstly, LLMs are not designed to generate XPath queries. Secondly, web pages are lengthy and complex, full of task unrelated information. Those information distract the LLMs from generating the correct XPath queries. Thirdly, LLMs are context limited. A good XPath query should be generalizable across different web pages. However, LLMs can only generate XPath queries based on the context they have seen. So, a shorter and more task-related context is more likely to generate a better XPath query.

Based on the above insights, we propose a novel approach to generate XPath queries using LLMs. We aim to reduce the number of steps required to generate a well-crafted XPath query, reduce the computational overhead, and improve the generalizability of the XPath queries generated by LLMs.

@@

We address each of the above motivations and make the following main contributions:

\begin{enumerate}
  \item We designed a two stage pipeline, which we can employ a week LLM to extract target information. And a stronger LLM to program XPath.
  \item We proposed a simple way to prune the web page, which can reduce the complexity of the web page and make the LLM focus on the target information.
  \item We discovered a cue text that share context between two stage significantly improve the performance of the XPath programming agent.
  \item We benchmarked our approach against a state-of-the-art XPath programming agent across a suite of web crawling tasks. Our findings reveal that our approach excels in F1 score with minimal compromise on accuracy, while significantly reducing token usage and increase clock-time efficiency.
\end{enumerate}
